Models

### 2023-01-17 analysis/05_model_metrics.Rmd
Fit individual studies using the appropriate response variable, deal with convergence stuff

# get dataframe of mixed effects models to fit
metric_df <- bind_rows(tibble(metric_name = metric_names[metric_names != "S"], 
                         formula = "value ~ year_scaled + (year_scaled|rarefyID)"),
          tibble(metric_name = c("S"), 
                         formula = "logvalue ~ year_scaled + (year_scaled|rarefyID)")) %>%
  mutate(model_id = "base")

@@

#get dataframe of glm's to fit
glm_indv_model_df <- single_ts %>% 
  mutate(model_id = "base",
         formula = "value ~ year_scaled")

@@

indv_mod_results <- bind_rows(mixed_indv_mod_results, glm_indv_mod_results)
```

>>>>

# get dataframe of mixed effects models to fit
metric_df <- bind_rows(tibble(metric_name = raw_metrics, 
                         formula = "value ~ year_scaled + (year_scaled|rarefyID)"),
          tibble(metric_name = logone_metrics, 
                         formula = "logvalue ~ year_scaled + (year_scaled|rarefyID)"),
          tibble(metric_name = log_metrics, 
                         formula = "log(value) ~ year_scaled + (year_scaled|rarefyID)")) %>%
  mutate(model_id = "base")

@@

# they didn't all converge
#get the models that had convergence warnings
bad_indv_models <- mixed_indv_mod_results %>%
  select(metric, model_id, study_id, warning) %>% 
  filter(!is.na(warning)) %>% 
  distinct() %>%
  left_join(mixed_indv_model_df, 
            by = c("metric" = "metric_name", "model_id", "study_id" = "filter_study_id")) %>%
  rename( filter_study_id = study_id)

#Turn off REML for these models, and they fit! 
bad_indv_results <- pmap_dfr(bad_indv_models %>% select(-warning), get_model, data = model_data, REML = FALSE) %>%
  mutate(REML = FALSE, bobyqa = FALSE)

#models that still won't converge
bad_indv_models2 <- bad_indv_results %>%
  select(metric, model_id, warning, study_id) %>% 
  filter(!is.na(warning)) %>% 
  distinct() %>%
  left_join(mixed_indv_model_df, 
            by = c("metric" = "metric_name", "model_id", "study_id" = "filter_study_id")) %>%
  rename( filter_study_id = study_id)

#Fit with a different algorithm
bad_indv_results2 <- pmap_dfr(bad_indv_models2 %>% select(-warning), get_model, data = model_data, control = lmerControl(optimizer = "bobyqa")) %>%
  mutate(REML = TRUE, bobyqa = TRUE)

##FIXME: some of these still don't converge##
```

Fit models for studies with only one time series
```{r}

#get dataframe of glm's to fit
glm_indv_model_df <- single_ts %>% 
  mutate(model_id = "base",
         formula = case_when(
           metric_name %in% raw_metrics ~ "value ~ year_scaled",
           metric_name %in% log_metrics ~ "log(value) ~ year_scaled",
           TRUE ~ "logvalue ~ year_scaled"
           )
         )

@@

indv_mod_results <- bind_rows(mixed_indv_mod_results %>% filter(is.na(warning)), 
          bad_indv_results %>% filter(is.na(warning)),
          bad_indv_results2 %>% filter(is.na(warning)),
          glm_indv_mod_results
          )
```
